Twisted 11-dimensional supergravity, I

### 2021-10-13 dimred.tex
ks merge

\section{Dimensional reduction and 10-dimensional supergravity}

@@

\subsection{Reduction to IIA supergravity}

@@

\parsec[sec:dimred]

@@

To this end, we consider placing 11-dimensional supergravity on the manifold $\CC^5 \times [0,1]$. 
In order to do this, we must choose appropriate boundary conditions at $t=0$ and $t=1$.

@@

In \cite{?} an explicit model has been given for the theory compactified along the slab for theories which are topological in the direction normal to the boundary.
The fields of the theory compactified on the slab is computed by the {\em derived} intersection of the two Lagrangians:
\[
\cM_{t=0} \overset{\LL}{\underset{\cE_{\del}}{\times}}\cM_{t=1}.
\]

@@

\begin{conj}
\label{conj:5dsugra}
The twist of 5d supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representation $V$ has BV fields
\begin{itemize}
\item $\alpha, A_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)$ with conjugate fields $\eta, B_{grav}$,
\item $A \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes \fg$ with conjugate field $B$,
\item $\chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes V$ with conjugate field $\psi$.
\end{itemize}

@@

Denote the full de Rham cohomology of $X$ by
\[
\cA(X) = H^\bu (X, \Omega^\bu) = \oplus_{i,j} H^i (X, \Omega^j_X)  .
\]
This is a graded commutative algebra using the wedge product of differential forms. 
Next, consider the space of holomorphic functions $\cO(\CC^2)$ on $\CC^2$. 
The Poisson bracket $\{-,-,\}$ associated to the standard holomorphic symplectic structure on $\CC^2$ endows $\cO(\CC^2)$ with the structure of a Lie algebra. 
In particular, we can tensor $\cO(\CC^2)$ with $\cA_X$ to obtain the structure of a graded Lie algebra on $\cA(X) \otimes \cO(\CC^2)$.

The global symmetry algebra of the compactified theory is a deformation of this graded Lie algebra. 
Let $[\omega] \in H^1(X, \Omega^1_X)$ be the class of the K\"ahler form on $X$. 
The deformation of $\cA(X) \otimes \cO(\CC^2)$ introduces the following Lie bracket 
\[
\big[ [\omega] \otimes f, [\omega] \otimes g\big] = [\omega^2] \otimes \{f,g\} \in H^{2,2}(X, \Omega^2) \otimes \cO(\CC^2) . 
\]

First, let's compute the global symmetry algebra of the twist of the pure gravity theory on $\CC^2 \times \RR$. 
This arises from terms in the BV action \eqref{eqn:5daction} involving only $\alpha, \eta, A_{grav}$, and $B_{grav}$.

The underlying graded vector space of the resulting Lie algebra is equivalent to
\[
\cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} .
\]
The non trivial Lie brackets are
%\begin{multline}
%[\alpha, \alpha'] = \{\alpha, \alpha'\} \in \cO(\CC^2)_\alpha , \quad [\alpha, \eta] = \{\alpha, \eta\} \in \cO(\CC^2)_\eta , \quad [\alpha, A_{grav}] = \{\alpha, A_{grav}\} \in \cO(\CC^2)_{A_{grav}} \\ 
%[\alpha, B_{grav}] = \{\alpha, B_{grav}\} \in \cO(\CC^2)_{B_{grav}} , \quad [B_{grav}, B'_{grav}] = \{B_{grav}, B'_{grav}\} \in \cO(\CC^2)_{A_{grav}} .
%\end{multline}
\begin{align*}
[\alpha, \alpha' + \eta + A_{grav} + B_{grav}] & = \{\alpha,  \alpha'\} + \{\alpha, \eta\} + \{\alpha, A_{grav}\} + \{\alpha, B_{grav}\} \\ & \in \cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} \\
[B_{grav}, B'_{grav}] & = \{B_{grav}, B'_{grav}\} \in \cO(\CC^2)_{A_{grav}} .
\end{align*}
Denote this Lie algebra by $\fg_{grav}$.

The contribution of the vector and hypermultiplets form a module for $\fg_{grav}$. 
As a graded vector space, this module is
\[
M_X = \cO(\CC^2) \otimes H^{1}(X, \Omega^1_X)_\perp [-1] \oplus \cO(\CC^2) \otimes 
\]

\subsection{The $SU(5)$ twist of type IIA supergravity}

@@

>>>>

\section{Dimensional reduction and 10-dimensional supergravity}
\label{sec:dimred}

@@

\subsection{Reduction to IIA supergravity}
\label{s:su4red}

@@

@@

We consider placing twisted 11-dimensional supergravity on the manifold $\CC^5 \times [0,1]$. 
In order to do this, we must choose appropriate boundary conditions at $t=0$ and $t=1$.
Our 11-dimensional theory on such manifolds fits nicely into the formalism of \cite{BY,Eugene} in that it is topological in the direction transverse to the boundary.

@@

An important thing to note is that the fields of the theory compactified on the slab is computed by the {\em derived} intersection of the two Lagrangians:
\[
\cM_{t=0} \overset{\LL}{\underset{\cE_{\del}}{\times}}\cM_{t=1}.
\]
To compute this derived intersection we must suitably resolve the boundary conditions.

@@

\begin{conj}
\label{conj:5dsugra}
The twist of 5d supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representation $V$ has BV fields
\begin{itemize}
\item $\alpha, A_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)$ with conjugate BV fields $\eta, B_{grav}$,
\item $A \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes \fg$ with conjugate BV field $B$,
\item $\chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes V$ with conjugate BV field $\psi$.
\end{itemize}

@@

Consider the full de Rham cohomology of $X$ by
\[
H^\bu (X, \Omega^\bu) = \oplus_{i,j} H^i (X, \Omega^j_X)  .
\]
This is a graded commutative algebra using the wedge product of differential forms. 
Next, consider the space of holomorphic functions $\cO(\CC^2)$ on $\CC^2$. 
The Poisson bracket $\{-,-,\}$ associated to the standard holomorphic symplectic structure on $\CC^2$ endows $\cO(\CC^2)$ with the structure of a Lie algebra. 
In particular, we can tensor $\cO(\CC^2)$ with $H^\bu (X, \Omega^\bu)$ to obtain the structure of a graded Lie algebra on 
\[
H^\bu (X, \Omega^\bu) \otimes \cO(\CC^2) .
\]
Let $[\omega] \in H^1(X, \Omega^1_X)$ be the class of the K\"ahler form on $X$.

The global symmetry algebra of the compactified theory along the Calabi--Yau three-fold $X$ is equivalent to a deformation of this graded Lie algebra. 
The deformation introduces the following Lie bracket 
\[
\big[ [\omega] \otimes f, [\omega] \otimes g\big] = [\omega^2] \otimes \{f,g\} \in H^{2,2}(X, \Omega^2) \otimes \cO(\CC^2) . 
\]

%\begin{proof}
%The computation of the global symmetry algebra of the 5-dimensional theory is very similar to the computation in the 11-dimensional theory.
%In terms of the de Rham cohomology, the generators of the linearized cohomology of the space of fields read:
%\begin{itemize}
%\item a holomorphic function $\alpha(z_1,z_2) \in H^0(X, \Omega^0) \otimes \cO(\CC^2)$.
%\item a 
%
%First, let's compute the global symmetry algebra of the twist of the pure gravity theory on $\CC^2 \times \RR$. 
%This arises from terms in the BV action \eqref{eqn:5daction} involving only $\alpha, \eta, A_{grav}$, and $B_{grav}$. 
%
%The underlying graded vector space of the resulting Lie algebra is equivalent to
%\[
%\cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} .
%\]
%The non trivial Lie brackets are
%\begin{multline}
%[\alpha, \alpha'] = \{\alpha, \alpha'\} \in \cO(\CC^2)_\alpha , \quad [\alpha, \eta] = \{\alpha, \eta\} \in \cO(\CC^2)_\eta , \quad [\alpha, A_{grav}] = \{\alpha, A_{grav}\} \in \cO(\CC^2)_{A_{grav}} \\ 
%[\alpha, B_{grav}] = \{\alpha, B_{grav}\} \in \cO(\CC^2)_{B_{grav}} , \quad [B_{grav}, B'_{grav}] = \{B_{grav}, B'_{grav}\} \in \cO(\CC^2)_{A_{grav}} .
%\end{multline}
%\begin{align*}
%[\alpha, \alpha' + \eta + A_{grav} + B_{grav}] & = \{\alpha,  \alpha'\} + \{\alpha, \eta\} + \{\alpha, A_{grav}\} + \{\alpha, B_{grav}\} \\ & \in \cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} \\
%[B_{grav}, B'_{grav}] & = \{B_{grav}, B'_{grav}\} \in \cO(\CC^2)_{A_{grav}} .
%\end{align*}
%Denote this Lie algebra by $\fg_{grav}$. 
%
%The contribution of the vector and hypermultiplets form a module for $\fg_{grav}$. 
%As a graded vector space, this module is
%\[
%M_X = \cO(\CC^2) \otimes H^{1}(X, \Omega^1_X)_\perp [-1] \oplus \cO(\CC^2) \otimes 
%\]
%\brian{incomplete}

\subsection{The $SU(5)$ twist of type IIA supergravity}
\label{s:su5IIA}

@@

We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the 10d $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}.

A minimal twisting supercharge $Q_{hol}$ in the $\cN=(1,1)$ super Poincar\'e algebra determines a maximal isotropic $L \subset \CC^{10}$. 
In a completely analogous way to the calculation for the twist of the algebra $\m2$ or the $SU(4)$ twist of the as in \cite{CLsugra} one can prove the following.

\begin{prop}
As an $\lie{sl}(5)$ representation the $Q_{hol}$-cohomology of $\lie{string}_{IIA}$ is equivalent
